\LARGE \bf Bidding-Based Autonomous Exploration of Cooperative Robots Building a 3D Probabilistic Occupancy Grid Map

### 2019-01-09 Conference/ACC 2019.2/ACC19.tex
added mars presentation

\documentclass[letterpaper, 10pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts \overrideIEEEmargins
\usepackage{amsmath,amssymb,url,times,subfigure,graphicx,theorem}
\usepackage{graphicx,subfigure,hyperref}
\usepackage{color,comment}
\usepackage{csquotes}
%\usepackage{refcheck}

@@

%\usepackage{algorithmicx}
%\usepackage{algpseudocode}

%\usepackage{algorithm}
%\usepackage{algpseudocode}
%\usepackage{pifont}

%\usepackage{amsmath}
%\usepackage{algorithm}
%\usepackage[noend]{algpseudocode}
%
%\makeatletter
%\def\BState{\State\hskip-\ALG@thistlm}
%\makeatother

%\definecolor{red}{rgb}{0,0,0}
\graphicspath{{../../Fig/}}

@@

\newcommand{\EditEK}[1]{{\color{blue}\protect #1}}
%\renewcommand{\EditTL}[1]{{\protect #1}}

@@

\begin{document}
\allowdisplaybreaks

@@

\begin{abstract}
This paper presents a bidding-based cooperative robotic exploration strategy to generate accurate occupancy grid maps with multiple vehicles. Using recent developments in 3D occupancy grid mapping and autonomous exploration, we propose an auction-based framework to build maps from various vantage points. A central executive reviews individual robot bids to maximize map information gain, and these bids are updated to prevent robots from capturing the same grid cells or colliding, which is further optimized with a receding horizon framework. Furthermore, considering a multi-agent system capable of large environmental coverage, several computational enhancements are presented to improve the scalability of the mapping and exploration algorithms. This multi-vehicle exploration approach is demonstrated with a numerical simulation where three robots simultaneously explore a large building floor plan cooperatively.
\end{abstract}

\section{Introduction}

% Multivehicle MAPPING in 3D 
% what is mapping?
% Occupancy grid mapping this way (ACC, JIRS, IRC)
% Designed to work with multiple sensors
% 
% Exploration:
% Frontier, entropy-based
% Recent papers (SIMPAR, JIRS, IRC)
% Main idea: maximizing a reward
% Multivehicle: 
%

@@

%In short, the robot with the largest bid wins the first auction, then discounts all candidate poses within a small neighborhood of the auction-winning robot, and this robot is removed from further auctions. This process is repeated, removing a robot from consideration each auction, until just a single robot remains.

@@

%              C++
%              if(distToOptimalPose < explore.discountRadius)
%                proximityDiscount = pow(distToOptimalPose/explore.discountRadius, 2);
%              else
%                proximityDiscount = 1.0;

%\begin{align}
%\label{eqn:bumpFun}
%\text{bump}(d_\text{cell})= 
%\begin{cases}
%    e^{1-\frac1{1-(d_\text{cell}/d_\text{max})^2}},			& \text{if }-d_\text{max}<d_\text{cell}<d_\text{max}\\
%    0,              				& \text{otherwise}
%\end{cases},
%\end{align}

@@

	\begin{figure}
		\centerline{
			\subfigure[Floor Plan]{\includegraphics[height=0.5\columnwidth]{SEH_cropped.png}}
			\hspace*{0.025\columnwidth}
			\subfigure[Gazebo Environment]{\includegraphics[height=0.5\columnwidth]{gazeboSEH.png}}
		}
		\caption{Simulated Environment of SEH}
			\label{fig:SEHEnvironment}
	\end{figure}

@@

	\begin{figure}
	% trim={<left> <lower> <right> <upper>}
		\centerline{
			\subfigure[$0$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_0min.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$1$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_1min.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\centerline{
			\subfigure[$2$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_2min.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$3$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_3min.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\centerline{
			\subfigure[$4$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_4min.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$5$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_5min.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\centerline{
			\subfigure[$6$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_6min.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$7$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_7min.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\centerline{
			\subfigure[$8$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_8min.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$9$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_9min.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\caption{2D Projected Occupancy Grid Map of SEH Second Floor}
			\label{fig:sim2Dmaps}
	\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

\usepackage{amsmath,amssymb,url,times,subfigure,graphicx,theorem}
\usepackage{graphicx,subfigure,hyperref}
\usepackage{color,comment}
\usepackage{csquotes}
%\usepackage{refcheck}

@@

\graphicspath{{../../Fig/}}

@@

@@

\begin{document}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

This paper presents a bidding-based cooperative robotic exploration strategy to generate accurate occupancy grid maps with multiple vehicles. Using recent developments in 3D occupancy grid mapping and autonomous exploration, we propose an auction-based framework to build maps from various vantage points. A central executive reviews individual robot bids to maximize map information gain, and these bids are updated to prevent robots from capturing the same grid cells or colliding, which is further optimized with a receding horizon framework. Furthermore, considering a multi-agent system capable of large environmental coverage, several computational enhancements are presented to improve the scalability of the mapping and exploration algorithms. This multi-vehicle exploration approach is demonstrated with a numerical simulation where three robots simultaneously explore a large building floor plan cooperatively.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

@@

@@

	\begin{figure}
		\centerline{
			\subfigure[Floor Plan]{\includegraphics[height=0.5\columnwidth]{SEH_cropped.jpeg}}
			\hspace*{0.025\columnwidth}
			\subfigure[Gazebo Environment]{\includegraphics[height=0.5\columnwidth]{gazeboSEH.png}}
		}
		\caption{Simulated Environment of SEH}
			\label{fig:SEHEnvironment}
	\end{figure}

@@

	\begin{figure}
	% trim={<left> <lower> <right> <upper>}
		\centerline{
			\subfigure[$0$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_0min_ss.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$1$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_1min_ss.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\centerline{
			\subfigure[$2$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_2min_ss.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$3$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_3min_ss.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\centerline{
			\subfigure[$4$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_4min_ss.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$5$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_5min_ss.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\centerline{
			\subfigure[$6$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_6min_ss.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$7$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_7min_ss.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\centerline{
			\subfigure[$8$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_8min_ss.jpg}}
			\hspace*{0.025\columnwidth}
			\subfigure[$9$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_9min_ss.jpg}}
		}
		\vspace*{0.025\columnwidth}
		\caption{2D Projected Occupancy Grid Map of SEH Second Floor}
			\label{fig:sim2Dmaps}
	\end{figure}
